A Meta-analysis of Longevity Estimates of Mosquito Vectors of Disease: Supplementary Figures

### 2021-05-17 writeUp/figures.tex
very nearly at a draft
updated order as per Charles comments
Updated text and a smartened a few figures

\begin{figure}[h]
	\centerline{\includegraphics[width=1\textwidth]{./Figure_files/dissection_lifetimes_exponential.pdf}}
	\caption{\textbf{Polovodova dissection: grouped physiological lifespan estimates.} The lifespans shown are for mosquitoes that were not fed with sugar or blood (for females) before release. The middle line in each box shows the median estimates and the solid dot indicates the mean. The left and right box edges show the 25\%, and 75\% posterior quantiles respectively. The whiskers show the range of the data, excluding points lying more than 1.5 times the interquartile range away from each edge of the box. The numbers before the start of the left whisker indicate the number of individual time-series within each species. All estimates were obtained using the hierarchical exponential survival model.}
	\label{fig:dissection_lifetimes_exponential}
\end{figure}

@@

@@

\begin{figure}[h]
	\centerline{\includegraphics[width=1.3\textwidth]{./Figure_files/detinova_gambiae_daynight_range_lifespan_country.pdf}}
	\caption{\textbf{Detinova dissection: day-night temperature range versus lifespan estimates for \textit{Anopheles gambiae s.l.}.} Points indicate the posterior mean estimates and the whiskers show 25\% and 75\% quantiles. Each blue line indicates a posterior estimate of the relationship between lifespan and temperature range; the orange line indicates the posterior median.}
	\label{fig:detinova_gambiae_daynight_range_lifespan_country}
\end{figure}

>>>>

@@

\begin{figure}[h]
	\centerline{\includegraphics[width=1\textwidth]{./Figure_files/dissection_lifetimes_exponential.pdf}}
	\caption{\textbf{Polovodova dissection: grouped physiological lifespan estimates.} The middle line in each box shows the median estimates and the solid dot indicates the mean. The left and right box edges show the 25\%, and 75\% posterior quantiles respectively. The whiskers show the range of the data, excluding points lying more than 1.5 times the interquartile range away from each edge of the box. The numbers before the start of the left whisker indicate the number of individual time-series within each species. All estimates were obtained using the hierarchical exponential survival model.}
	\label{fig:dissection_lifetimes_exponential}
\end{figure}

@@

\begin{figure}[h]
	\centerline{\includegraphics[width=1.3\textwidth]{./Figure_files/detinova_gambiae_temp_range_lifespan.pdf}}
	\caption{\textbf{Detinova dissection: day-night temperature range versus lifespan estimates for \textit{Anopheles gambiae s.l.}.} Points indicate the posterior mean estimates and the whiskers show 25\% and 75\% quantiles. Each blue line indicates a posterior estimate of the relationship between lifespan and temperature range; the orange line indicates the posterior median.}
	\label{fig:detinova_gambiae_daynight_range_lifespan_country}
\end{figure}

### 2021-05-17 writeUp/supplementary_materials.tex
Updated text and a smartened a few figures

@@

\begin{figure}[h]
	\centerline{\includegraphics[width=1\textwidth]{./Figure_files/mrr_genus_vs_species_vs_top.pdf}}
	\caption{\textbf{MRR: predictive accuracy of the species- and overall-level models relative to the genus-level model.} The predictive accuracy was determined using K-Fold cross-validation as described in SOM; the measure of accuracy presented here by the central dots is the difference in estimated expected log pointwise predictive density compared to the exponential model. The lower and upper whiskers represent the lower and upper bounds of the 95\% confidence interval in predictive accuracy.}
	\label{fig:mrr_genusTopLevel}
\end{figure}

\begin{figure}[h]
	\centerline{\includegraphics[width=1\textwidth]{./Figure_files/mrr_female_blood_sugar.pdf}}
	\caption{\textbf{MRR: female mosquito mean lifespan by pre-release feeding status.} The lifespans shown are for mosquitoes that were not fed with sugar or blood (for females) before release. The middle line in each box shows the median estimates and the solid dot indicates the mean. The left and right box edges show the 25\%, and 75\% posterior quantiles respectively. The whiskers show the range of the data, excluding points lying more than 1.5 times the interquartile range away from each edge of the box. The numbers before the start of the left whisker indicate the number of individual time-series within each species. All estimates were obtained using the hierarchical exponential survival model.}
	\label{fig:mrr_female_blood_sugar}
\end{figure}

@@

\begin{figure}[h]
	\centerline{\includegraphics[width=1\textwidth]{./Figure_files/mrr_lifespanVsTrapDensity.pdf}}
	\caption{\textbf{MRR: mean mosquito lifespan versus trapping density.} The markers show the median posterior lifespan estimates for each time series with the lower and upper bounds indicating the 25\% and 75\% quantiles, respectively. The trap density was estimated assuming traps were contained within a circular area with radius equal to the trapping range. The black line shows a linear regression line estimated using the median posterior lifetimes, with the grey shading indicating 95\% confidence intervals. All estimates were obtained using the non-hierarchical exponential survival model.}
	\label{fig:mrr_lifeSpanVsTrapDensity}
\end{figure}

@@

\begin{figure}[h]
	\centerline{\includegraphics[width=1.3\textwidth]{./Figure_files/dissection_individualEstimates_allSpecies.pdf}}
	\caption{\textbf{Polovodova dissection: individual time-series estimates of adult mosquito mean lifespan.} The middle line in each box shows the median estimates. The left and right box whiskers show the 25\%, and 75\% posterior quantiles respectively. All estimates were obtained using the non-hierarchical exponential survival model.}
	\label{fig:dissection_individualEstimates_allSpecies}
\end{figure}

@@

>>>>

\begin{table}[htbp]
	\begin{tabular}{l|l|l|l|l}
		\textbf{Analysis} & \textbf{Grouping} & \textbf{Log-likelihood} & \textbf{z} & \textbf{p}\\
		\hline
		MRR & genus & -7315.2 & - & -\\
		& overall & -7511.0 & 11.3 & 0.0\\
		& species & -7748.9 & 5.5 & 0.0\\
		\hline
		Detinova & species & -14,672.4 & - & -\\
		& species-complex & -15,504.9 & 3.6 & 0.0\\
		& continent & -16,731.1 & 0.4 & 0.3\\
		\hline
		Polovodova & species & -3818.3 & - & -\\
		& genus & -3848.3 & 0.4 & 0.3\\
		& overall & -3895.5 & 0.4 & 0.4\\
	\end{tabular}
		\caption{\textbf{Model comparison by K-fold cross-validation.} Here, we present the estimates of model fit on hold-out datasets (see SOM) as measured by the sum of the pointwise log-likelihood values averaged across all posterior draws (in the ``Log-likelihood'' column) across each of the three analyses and each grouping of studies considered. Within each row-block (``MRR'', ``Detinova'', ``Polovodova''), the models are arranged according to the point estimate of the fit: best at top; worst at bottom. The $z$ scores show the scaled difference in the averaged pointwise log-likelihood \citep{vehtari2015efficient} versus the model immediately above it in the ranking, and the ``p'' column shows the corresponding $p$ values representing the cumulative density function from a standard normal.}
\end{table}

@@

\begin{figure}[h]
	\centerline{\includegraphics[width=1\textwidth]{./Figure_files/mrr_female_blood_sugar_inkscaped.pdf}}
	\caption{\textbf{MRR: female mosquito mean lifespan by pre-release feeding status.} Labels to the left of the vertical axis indicate genus or overall grouping; the labels to the right of the axis indicate pre-release feeding status. The middle line in each box shows the median estimates and the solid point indicates the mean. The left and right box edges show the 25\%, and 75\% posterior quantiles respectively. The whiskers show the range of the data, excluding points lying more than 1.5 times the interquartile range away from each edge of the box. All estimates were obtained using the hierarchical exponential survival model.}
	\label{fig:mrr_female_blood_sugar}
\end{figure}

@@

@@

@@

\bibliographystyle{authordate1}
\bibliography{Malaria}
